How it's been doing a statistics PhD plus some research

### 2022-01-30 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
Progressing presentation some more based on comments

@@

## Reflections on PhD experience

* Many (all?) of my friends doing PhDs have had periods where it has negatively effected them
  * "The well-being costs of graduate school versus STIs"
* Little structure, often sporadic feedback, uncertainty about research direction and progress, making a narrow contribution (that perhaps few people care about) to a large field
* Different to undergraduate: not learning material then passing test for another 3/4 years

@@

* HIV/AIDS is an infectious disease which is endemic in sub-Saharan Africa
* Epidemic indicators can be used to guide policy response
* My area of research is Bayesian spatio-temporal statistics, the method we use to perform small-area estimation
  * (I'll explain what these terms mean)

@@

@@

## Career plans going forward

* Global health
* Biosecurity
  * Reading group this term, Fridays at St Mary's 12-1!

>>>>

## Is it worth doing a PhD?

* Skills or talent gap for many causes in EA
  * Rather than funding gap
* Independent research skills developed during a PhD important for many causes
  * AI, biorisk, global priorities, global health and development
* Can be useful for signalling expertise
  * Then transfer into e.g. policy
* 3/4+ years, possibly large opportunity cost

@@

## Some negative reflections on PhD experience

* I, along with many (all?) of my friends doing PhDs, have had periods where it has negatively effected wellbeing
  * "Grad school is worse for public health than STDs" https://www.benkuhn.net/grad/
* Little structure, often sporadic feedback, uncertainty about research direction and progress, narrow contribution (that perhaps few people care about) to a large field, low pay, alignment with supervisor and program, (in some fields) somewhat pyramid scheme-y
* Different to undergraduate: not learning material then passing test for another 3/4 years

@@

* HIV/AIDS is an infectious disease which is endemic in sub-Saharan Africa
* Epidemic indicators can be used to guide policy response
  * Prevalence (how many people are infected)
  * Incidence (how many people newly infected)
  * Coverage of treatments (how many people have (don't have) treatment)
* My area of research is Bayesian spatio-temporal statistics, the method we use to perform small-area estimation
  * (I'll explain what these terms mean)

@@

## How impactful is this work

* Could be used to guide HIV interventions for women 15-29
  * Interventions suggested include STI-screening and treatment, economic empowerment, comprehensive sexuality education, PrEP, PEP
* Neglectedness, tractability, scale?
* TO-DO: Add the latest versions of infections averted graph

@@

## Some possible routes for the future

* Small-area estimation of health and development indicators
* Outbreak disease surveillance
* Monitoring of the environment (e.g. sea-ice for climate, air-pollution for global health)
* Statistical ecology (as it relates to animal welfare)
* AI safety (likely the more applied FAT-style work than theoretical)
* Predicting (or helping to win) elections
* Meta EA

## Current plan

* Outbreak disease surveillance for reducing GCBRs
* Longtermist issues likely score better on neglectedness and scope
* Biorisk cause area "competitive" with AI risk
  * Better personal fit to biorisk
* Biosecurity reading group this term, Fridays at St Mary's 12-1!
